---
title: "Data Exploration"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Exploration

Before building the classifier, it can be constructive to explore and visualize the data.

```{r}
library(tidyverse)
```

## Dataset

Using the classic Iris Dataset

```{r}
df <- as_tibble(iris)
str(df)
```

```{r}
head(df)
```

## Basic EDA

Prepare three dataframes

- df contains information for each flower
- df_long contains information for each measurement
- df_wide contains information for each part

```{r}
df_long <- df %>% 
    gather(key = Part_Measure, value = Value, -Species) %>% #Gather columns
    separate(col = Part_Measure, into = c("Part", "Measure"), sep = "\\.") #Break gathered column into two columns
df_long$Measure <- as.factor(df_long$Measure)
head(df_long)
```

```{r}
df$FlowerID <- 1:nrow(df)
df_wide <- df %>% 
    gather(key = Part_Measure, value = Value, -Species, -FlowerID) %>% 
    separate(col = Part_Measure, into = c("Part", "Measure"), sep = "\\.") %>% 
    spread(key = Measure, value = Value)
head(df_wide)
```

Q: How do measurements compare between species?

```{r}
ggplot(df_long, aes(x = Species, y = Value, col = Part)) +
    geom_jitter()+
    facet_grid(. ~ Measure)
```

Right away, we can see that the Setosa is distinct from the other two species, especially by Petal.
The sepal measurements between the Versicolor and Virginica species appear similar, especially for width
Q: How does length and width of each part relate for each species?


```{r}
ggplot(df_wide, aes(x = Length, y = Width, col = Part)) +
    geom_jitter() +
    facet_grid(. ~ Species)
```

Q: How do the species compare to each other?
```{r}
ggplot(df_wide, aes(x=Length, y = Width, col = Species)) +
    geom_jitter() +
    facet_grid(. ~ Part)
```

Petal measurements are distinct between each species.
Sepal widths of Virginica and Versicolor overlap but values of length vary.

Wonderings:
- can a simple neural network be trained to distinguish flower species?

Answer:
- Definitely, although mileage may vary.